%%% ---------------------------------------------------------------
%%% FORECAST COMBINATION / PROBABILISTIC FORECASTING LITERATURE
%%% ---------------------------------------------------------------

\bibitem{clemen89}
Robert T. Clemen.
\textit{Combining Forecasts: A Review and Annotated Bibliography}.
International Journal of Forecasting, 5(4):559--583, 1989.

\bibitem{ranjan10}
Roopesh Ranjan and Tilmann Gneiting.
\textit{Combining Probability Forecasts}.
Journal of the Royal Statistical Society, Series B, 72(1):71--91, 2010.

\bibitem{gneiting13}
Tilmann Gneiting and Roopesh Ranjan.
\textit{Combining Predictive Distributions}.
Electronic Journal of Statistics, 7:1747--1782, 2013.

\bibitem{clements06}
Michael~P. Clements.
\textit{Evaluating the Survey of Professional Forecasters Probability
  Distributions for Inflation and Output Growth}.
Empirical Economics, 31(1):49--64, 2006.

\bibitem{lahiri15}
%%% TODO: Verify full author list and exact title — confirmed IFJ 31(1):113-129, 2015
Kajal Lahiri, Herman Peng, and Xuguang Sheng.
\textit{Measuring Uncertainty of a Combined Forecast and Some Tests for Forecaster Heterogeneity}.
International Journal of Forecasting, 31(1):113--129, 2015.

\bibitem{wang23}
%%% TODO: Verify full author list — confirmed: Wang, Hyndman, Li, Kang (2023)
Xiaoqian Wang, Rob~J. Hyndman, Feng Li, and Yanfei Kang.
\textit{Forecast Combinations: An Over 50-Year Review}.
International Journal of Forecasting, 39(4):1518--1547, 2023.

\bibitem{mcandrew21}
%%% TODO: Verify full author list and exact journal details
Thomas McAndrew and Nicholas~G. Reich.
\textit{Aggregating Predictions from Experts: A Review of Statistical Methods, Experiments, and Applications}.
WIREs Computational Statistics, 2021.

\bibitem{lecoz23}
%%% TODO: Verify exact year, venue, and page range — arXiv or journal
Cyril Le~Coz, Amaury Lam{\'e}nicht, and Ali~Ayoub.
\textit{Wasserstein Barycenter-Based Ensemble Weather Forecast Combination}.
arXiv preprint, 2023.

\bibitem{taylor26}
%%% TODO: Verify exact year (may be 2024/2025) and journal
James~W. Taylor.
\textit{Probabilistic Forecast Aggregation Using Statistical Depth}.
Working paper, 2026.

\bibitem{genest86}
C. Genest and J.V. Zidek.
\textit{Combining Probability Distributions: A Critique and an Annotated Bibliography}.
Statistical Science, 1(1):114-135, 1986.

\bibitem{genest90}
C. Genest and K.J. McConway.
\textit{Allocating the Weights in the Linear Opinion Pool}.
Journal of Forecasting, 9(1):53-73, 1990.

\bibitem{gneiting07}
Tilmann Gneiting and Adrian E. Raftery.
\textit{Strictly Proper Scoring Rules, Prediction, and Estimation}.
Journal of the American Statistical Association, 102(477):359-378, 2007.

\bibitem{ohagan06}
A. O'Hagan, C.E. Buck, A. Daneshkhah, J.R. Eiser, P.H. Garthwaite,
D.J. Jenkinson, J.E. Oakley, and T. Rakow.
\textit{Uncertain Judgements: Eliciting Experts' Probabilities}.
John Wiley \& Sons, Chichester, 2006.

\bibitem{panaretos19}
Victor M. Panaretos and Yoav Zemel.
\textit{Statistical Aspects of Wasserstein Distances}.
Annual Review of Statistics and Its Application, 6:405-431, 2019.

\bibitem{satopaa14}
Ville A. Satop{\"a}{\"a}, Jonathan Baron, Dean P. Foster, Barbara A. Mellers,
Philip E. Tetlock, and Lyle H. Ungar.
\textit{Combining Multiple Probability Predictions Using a Simple Logit Model}.
International Journal of Forecasting, 30(2):344-356, 2014.

\bibitem{timmermann06}
Allan Timmermann.
\textit{Forecast Combinations}.
In G. Elliott, C.W.J. Granger, and A. Timmermann (Eds.),
\textit{Handbook of Economic Forecasting}, Volume 1, pages 135-196.
Elsevier, Amsterdam, 2006.

\bibitem{agueh2011barycenters}
Martial Agueh, Guillaume Carlier.
\textit{Barycenters in the Wasserstein Space}.
SIAM Journal on Mathematical Analysis, 43(2):904-924, 2011.

\bibitem{aitch82}
John Aitchison.
\textit{The statistical analysis of compositional data}.
Journal of the Royal Statistical Society. Series B (Methodological), 44(2):139-177, 1982.

\bibitem{aitch85}
John Aitchison.
\textit{A General Class of Distributions on the Simplex}.
Journal of the Royal Statistical Society. Series B (Methodological), 47(1):136-146, 1985.


\bibitem{dbary}
Ethan Anderes, Steffen Borgwardt, Jacob Miller.
\textit{Discrete Wasserstein Barycenters: Optimal Transport for Discrete Data}.
Mathematical Methods of Operations Research, 84(2):389-409, 2016.

\bibitem{concen_blm}
St{\'e}phane Boucheron, G{\'a}bor Lugosi, and Pascal Massart.
\textit{Concentration Inequalities: A Nonasymptotic Theory of Independence}.
Oxford University Press, 2013.

\bibitem{carterette}
Ben Carterette.
\textit{On Rank Correlation and the Distance Between Rankings.}
Proceedings of the 32nd international ACM SIGIR conference on Research and development in information retrieval. ACM, 436-443, 2009.

\bibitem{schen}
Shuo Chen and Thorsten Joachims.
\textit{Modeling Intransitivity in Matchup and Comparison Data}.
Proceedings of the 9th ACM International Conference on Web Search and Data Mining, 2016.

\bibitem{cuturi}
Marco Cuturi and Arnaud Doucet.
\textit{Fast Computation of Wasserstein Barycenters}.
Proceedings of the 31st International Conference on Machine Learning, Beijing, China, 2014. JMLR: W\&CP, Volume 32.

\bibitem{advcalc}
Patrick M. Fitzpatrick.
\textit{Advanced Calculus}.
Thompson Brooks/Cole, Belmont, 2006.

\bibitem{geyer}
Charles J. Geyer.
\textit{Markov Chain Monte Carlo Maximum Likelihood.}
Interface Foundation of North America. Retrieved from the University of Minnesota Digital Conservancy, http://hdl.handle.net/11299/58440, 1991.

\bibitem{hinton02}
G.E. Hinton.
\textit{Training products of experts by minimizing contrastive divergence.}
Neural Computation, 14:1771-1800, 2002.

\bibitem{kumar}
Ravi Kumar and Sergei Vassilvitskii.
\textit{Generalized Distances between Rankings}.
Proceedings of the 19th international conference on World wide web. ACM, 571-580, 2010.

\bibitem{linderman}
Scott W. Linderman, Ryan P. Adams.
\textit{Discovering Latent Network Structure in Point Process Data}.
In International Conference on Machine Learning, 1413-1421, 2014.

\bibitem{minka}
Thomas Minka.
\textit{Estimating a Dirichlet distribution}.
Technical Report, MIT, 2000.


\bibitem{copulaRN}
Roger B. Nelsen.
\textit{An Introduction to Copulas}.
Springer Science \& Business Media, 2007.

\bibitem{ng}
Kai Wang Ng, Guo-Liang Tian, and Man-Lai Tang.
\textit{Dirichlet and related distributions: Theory, methods and applications}. 
Vol. 888. John Wiley \& Sons, 2011.

\bibitem{yuille}
Alan L. Yuille.
\textit{The convergence of contrastive divergences}.
Advances in neural information processing systems, 1593-1600, 2005.
