%% Journal of Forecasting submission draft
\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage[left]{lineno}

\doublespacing
\linenumbers

%% Math operators
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\Var}{Var}
\DeclareMathOperator*{\supp}{supp}

%% Theorem environments
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}

\numberwithin{equation}{section}

\begin{document}

\title{Robust Aggregation of Expert Probability Forecasts\\
       via Wasserstein Barycenters}

\author{Aaron J. Danielson\thanks{Corresponding author.
        \textit{Email:} [add email].
        \textit{Address:} [add affiliation].}\\[0.5ex]
        [add affiliation]
        \and
        Arash A. Amini\\[0.5ex]
        [add affiliation]}

\date{}
\maketitle

\begin{abstract}
We study the aggregation of expert probability forecasts over a finite outcome space.
The standard approach, the arithmetic mean (linear opinion pool), is sensitive to extreme opinions: a minority assigning substantial mass to tail outcomes can distort the aggregate away from the majority view.
We propose the Wasserstein barycenter as a robust alternative.
Under the indicator ground cost the barycenter reduces to an $\ell^1$ aggregation problem; for ordered outcome spaces it admits a closed form---the distribution whose CDF is the component-wise median of the individual CDFs---computable without a solver.
We validate the framework across three datasets.
On 94 binary questions from the Good Judgment Project ($\sim\!900$ forecasters each), the barycenter reduces mean Brier score by 12.5\% relative to the arithmetic mean ($p < 0.001$).
On 76 quarters of U.S.\ Survey of Professional Forecasters core CPI histograms (2007--2025), benchmarked against the arithmetic mean, logarithmic pool, and trimmed mean, the barycenter and trimmed mean both achieve lower mean RPS than the arithmetic mean ($p < 0.01$, Wilcoxon), with the advantage concentrated in low-dispersion quarters; the logarithmic pool has the highest P(correct bin) but worst RPS, a divergence explained by the $\ell^1$--$\ell^2$ mismatch between the pooling objective and the scoring rule.
A replication on the ECB Survey of Professional Forecasters confirms the dispersion-conditional pattern across the Euro-area panel.
A dispersion-adaptive convex blend achieves the lowest out-of-sample forecast score in the historical evaluation.
Simulation evidence characterizes the robustness--efficiency tradeoff and identifies conditions under which each method is preferred.
\end{abstract}

\bigskip
\noindent\textbf{Keywords:} forecast combination; opinion pooling; Wasserstein distance;
optimal transport; Survey of Professional Forecasters; robust aggregation

\bigskip
\noindent\textbf{JEL codes:} C53, C44, D83

\newpage

\input{DiscreteBarycenter}

\begin{thebibliography}{99}
\input{barybib}
\end{thebibliography}

\end{document}
